The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-10-14 paper/Analisis.tex
Merged Anisotropic emission section with Off-center section

\subsection{Anisotropic emission}

In Figure \ref{fig:flux} we show the angular dependency of the flux for the
central (left) and homogeneous (right) source distributions. This
shows that observers at different directions would infer luminosities
different from the isotropical value only at levels $< 3\%$.

\begin{figure*}
\includegraphics[scale=0.3]{mu_central.png}
\includegraphics[scale=0.3]{mu_homogeneous.png}
\caption{Flux angular dependency for the central (left) and homogeneous
(right) source distributions, different line widths illustrate different
rotational velocities.
   \label{fig:flux}} 
\end{figure*}

@@

As a primer approach we study the angular dependency in the same manner as
we do in section \ref{sec:results}, but with the set up of the off-center models
where the galaxy is rotating around the  $\hat{\textbf{z}}$ axis and the observer is 
located at $\mathrm{\theta = \pi/2}$. In Fig. \ref{fig:OCflux} the angular 
dependency for two different off-center distribution are shown. The bold line  
represents an off-center sphere located at $0.25 R$ in the homogeneous sphere, while 
the narrow line shows a sphere located at $-0.25 R$. This is done for the model 
with $\tau=10^{5}$ and $V=50 km s^{-1}$, but results with the rest of models
show exactly the same trend. We find a high dependency in the viewing angle
in particular the flux at $\mathrm{\theta = \pi/2}$ is $\simeq 88\%$ stronger than 
at $\mathrm{\theta = \pi/3}$ this have important consequences in observations when 
galaxies are oriented in random directions which implies that off-center emission
is not going to be observed in all the observed galaxies.

@@

%\begin{figure}
%\includegraphics[scale=0.3]{OC_5t_vel100.jpg}
%\caption{Spectra for two off-center spheres
%   \label{fig:OCspectra}} 
%\end{figure}

>>>>

@@

For the central and homogeneous source distributions we find
that observers at different directions do not present an angular 
dependency, in particular they would infer luminosities
different from the isotropical value only at levels $< 3\%$.

But with the set up of the off-center models
where the galaxy is rotating around the  $\hat{\textbf{z}}$ axis and the observer is 
located at $\mathrm{\theta = \pi/2}$ we do find and angular dependency for both  
off-center distributions, this is shown in Fig. \ref{fig:OCflux}. The bold line  
represents an off-center sphere located at $0.25 R$ in the homogeneous sphere, while 
the narrow line shows a sphere located at $-0.25 R$. This is done for the model 
with $\tau=10^{5}$ and $V=50 km s^{-1}$, but results with the rest of models
show exactly the same trend. We find a high dependency in the viewing angle
in particular the flux at $\mathrm{\theta = \pi/2}$ is $\simeq 88\%$ stronger than 
at $\mathrm{\theta = \pi/3}$ this have important consequences in observations when 
galaxies are oriented in random directions which implies that off-center emission
is not going to be observed in all the observed galaxies.

@@
